The Design and Implementation of the Synchronous Language \CEU

### 2016-10-01 paper.tex
(>) stack/lexical/deterministic

\CEU aims to offer a simpler semantics than Esterel with more determinism and 
fine-grained control over program execution.
%
The following list summarizes the contributions of our design in this 
direction:
%
\begin{itemize}
%
\item \emph{Event-triggered notion of time bound to the semantics of the 
language.}
Event-driven programming is popular in many domains, such as server and GUI 
development.
We believe that programmers are more familiar with dealing with events in 
isolation, which simplifies the reasoning about concurrency.
In addition, the uniqueness of external events is a prerequisite for the 
concurrency checks of \CEU.
%
\item \emph{Deterministic intra-reaction execution and communication.}
Determinism in \CEU is ``all-inclusive'' and does not depend on additional 
levels of static analysis.
It encompasses the whole language, including memory accesses, system calls, and 
stack-based internal events.
Programmers can always figure out which statement executes next, making runtime 
analysis and debugging easier.
%
\item \emph{Static concurrency checks.}
Although execution is deterministic, the \CEU compiler still advises about 
suspicious statements that can react concurrently to the same event. 
%appropriate serialization.
%
\item \emph{Safe integration with \C.}
When dealing with concurrent system calls, programmers can provide annotations 
to reduce false positives in the static checks, or to force non commutative 
concurrent behavior.
\CEU also requires finalization clauses to handle pointers representing 
resources.
%
\item \emph{First-class timers with dedicated syntax and automatic 
synchronization.}
Given the omnipresence of timers in embedded systems, a dedicated syntax can 
simplify the development and readability of programs.
Furthermore, automatic synchronization releases the programmer from the burden 
of adjusting timers in sequence and in parallel.
%
\end{itemize}

>>>>

\CEU aims to offer a simpler semantics than Esterel with more determinism and 
fine-grained control over program execution.
%
The following list summarizes the contributions of our design in this 
direction:
%
\begin{itemize}
%
\item \emph{Event-triggered notion of time bound to the semantics of the 
language.}
Event-driven programming is popular in many domains, such as server and GUI 
development.
We believe that programmers are more familiar with dealing with events in 
isolation, which simplifies the reasoning about concurrency.
In addition, the uniqueness of external events is a prerequisite for the 
concurrency checks of \CEU.
%
\item \emph{Deterministic intra-reaction execution and communication.}
Determinism in \CEU does not depend on additional levels of static analysis.
It encompasses the whole language, including memory accesses, system calls, and 
stack-based internal events.
Programmers can always figure out which statement executes next, making runtime 
analysis and debugging easier.
%
\item \emph{Static concurrency checks.}
Although execution is deterministic, the \CEU compiler still advises about 
suspicious statements that can react concurrently to the same event. 
%appropriate serialization.
%
\item \emph{Safe integration with \C.}
When dealing with concurrent system calls, programmers can provide annotations 
to reduce false positives in the static checks, or to force non commutative 
concurrent behavior.
\CEU also requires finalization clauses to handle pointers representing 
resources.
%
\item \emph{First-class timers with dedicated syntax and automatic 
synchronization.}
Given the omnipresence of timers in embedded systems, a dedicated syntax can 
simplify the development and readability of programs.
Furthermore, automatic synchronization releases the programmer from the burden 
of adjusting timers in sequence and in parallel.
%
\end{itemize}
